Glucose ingestion before and after resistance training does not augment ribosome biogenesis in healthy moderately trained young adults

### 2023-09-29 README.rmd
fixe on ejap figs

# Repository organization and extended methods: *Glucose ingestion before and after resistance training does not augment ribosome biogenesis in healthy moderately trained young adults*

>>>>

# Extended methods: *Glucose ingestion before and after resistance training does not augment ribosome biogenesis in healthy moderately trained young adults*
